Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/relwk.tex
x

Proper input recognition has been shown to be an excellent way of
eliminating ambiguous inputs.  In one case, a PDF parser (implemented
in Coq) rejects over $95\%$ of known malicious PDFs by checking
whether they conform to the PDF format~\cite{Bogk-PDF}. The same project
also produced a ``counter-example'' PDF that triggered numerous bugs
in other PDF parsers. However, manually writing parser code and proving
unambiguity does not scale to the number of file formats and protocols
in existence and might result in parser code tied to one specific
application. By supporting a wide range of real-world file formats,
Nail helps programmers produce precise parsers for complex grammars.

>>>>

Proper input recognition has been shown to be an excellent way of
eliminating ambiguous inputs.  In one case, a PDF parser (implemented
in Coq) was used to reject over $95\%$ of known malicious PDFs by checking
whether they conform to the PDF format~\cite{Bogk-PDF}. The same project
also produced a ``counter-example'' PDF that triggered numerous bugs
in other PDF parsers. However, manually writing parser code and proving
unambiguity does not scale to the number of file formats and protocols
in existence and might result in parser code tied to one specific
application. By supporting a wide range of real-world file formats,
Nail helps programmers produce precise parsers for complex grammars.
